Concurrent Programming in Harmony

### 2021-12-25 book/paper.tex
Pass over Chapter 22

You would be excused if you wanted to solve the problem using locks, similar to
\autoref{fig:incfixed}.  \autoref{fig:trap3} shows how one might go about this.
But locks are intended to solve synchronization issues between multiple threads.
If you run the code through Harmony, you will find that the code may not terminate.
The issue is that a thread can only acquire a lock once.  If the interrupt happens
after <{main()}> acquires the lock but before <{main()}> releases it, the
<{handler}>() method will block trying to acquire the lock, even though
it is being acquired by the same thread that already holds the lock.

@@

There is another important rule to keep in mind.  Just like locks should never be held
for long, interrupts should never be disabled for long.  With locks the issue is to
maximize concurrent performance.  For interrupts the issue is fast response to
asynchronous events.  Because interrupts may be disabled only briefly, interrupt
handlers must run quickly and cannot wait for other events.  It is ok to invoke
non-blocking synchronization calls such as <{notify}>, but calls such as
<{acquire}> and <{wait}> should only be used if it is certain that they will not
block for long.  Informally, interrupt handlers can be
\emph{producers} but not \emph{consumers} of synchronization events.

>>>>

You would be excused if you wanted to solve the problem using locks,
similar to \autoref{fig:incfixed}.  \autoref{fig:trap3} shows how
one might go about this.  But locks are intended to solve synchronization
issues between multiple threads.  But an interrupt handler is not
run by another thread---it is run by the same thread that experienced
the interrupt.  If you run the code through Harmony, you will find
that the code may not terminate.  The issue is that a thread can
only acquire a lock once.  If the interrupt happens after <{main()}>
acquires the lock but before <{main()}> releases it, the <{handler}>()
method will block trying to acquire the lock, even though it is
being acquired by the same thread that already holds the lock.

@@

There is another important rule to keep in mind.  Just like locks should never be held
for long, interrupts should never be disabled for long.  With locks the issue is to
maximize concurrent performance.  For interrupts the issue is fast response to
asynchronous events.  Because interrupts may be disabled only briefly, interrupt
handlers must run quickly and cannot wait for other events.
\begin{comment}
It is ok to invoke
non-blocking synchronization calls such as <{notify}>, but calls such as
<{acquire}> and <{wait}> should only be used if it is certain that they will not
block for long.  Informally, interrupt handlers can be
\emph{producers} but not \emph{consumers} of synchronization events.
\end{comment}
